Visualization

### 2020-11-20 analysis/visualization.Rmd
Modify column names to match new dataframe.

```{r}
load(here::here("data", "biotime_data.rda"))
```

@@

plot_metric <- function(metric_name, ylabel){
  data <- fd_table %>%
    filter(metric == metric_name) %>%
    mutate(plot_id = as.factor(plot_id), logSES = log(SES))

  mod <- lmer(logSES ~ year + (1|plot_id), data = data)
  coefs <- summary(mod)$coefficients

@@

  trend_plot <- data %>%
    left_join(pred, by = "year") %>%
    #left_join(metadata %>% select(study_id, climate)) %>%
    ggplot(aes(x = year, y = logSES)) +
    # geom_smooth(aes(color = climate, group = plot_id), method = "glm", se = FALSE) +
    # geom_point(aes(color = climate, group = plot_id)) +
    geom_point(aes(group = plot_id) ,color = "grey") +
    geom_smooth(aes(group = plot_id), color = "darkgrey", method = "glm", se = FALSE) +
    #geom_smooth(color = "black", method = "glm", se = FALSE) +
    geom_line(mapping = aes(y = pred)) +
    theme(legend.position = "none") +
    theme_classic() +
    ylab(ylabel)

@@

get model info
```{r}
get_metric_conint <- function(metric_name){
 data <- fd_table %>%
    filter(metric == metric_name) %>%
    mutate(plot_id = as.factor(plot_id), logSES = log(SES))

  mod <- lmer(logSES ~ year + (1|plot_id), data = data)
  coefs <- summary(mod)$coefficients

>>>>

```{r}
metrics <- pins::pin_get("rarefied-medians", board = "github") %>%
  pivot_longer(., cols = setdiff(everything(), one_of("rarefyID", "STUDY_ID", "SamplePool", "SampleN", "num_years", "duration", "startYear", "endYear", "YEAR", "cell", "rarefied", "type", "realm", "climate", "habitat", "biome_map", "taxa", "organisms", "cent_lat", "cent_long", "abundance_type", "BROAD_TYPE", "cYEAR", "taxa_mod", "climate_mod")), names_to = "metric", values_to = "value") %>%
  rename_with(tolower, .cols = setdiff(everything(), one_of("rarefyID"))) 
```

@@

plot_metric <- function(metric_name, ylabel){
  data <- metrics %>%
    filter(metric == metric_name, !is.na(value), !is.infinite(value)) %>%
    mutate(logvalue = log(value))

  mod <- lmer(logvalue ~ year + (1|rarefyID), data = data)
  coefs <- summary(mod)$coefficients

@@

  trend_plot <- data %>%
    left_join(pred, by = "year") %>%
    #left_join(metadata %>% select(study_id, climate)) %>%
    ggplot(aes(x = year, y = logvalue)) +
    # geom_smooth(aes(color = climate, group = rarefyID), method = "glm", se = FALSE) +
    # geom_point(aes(color = climate, group = rarefyID)) +
    geom_point(aes(group = rarefyID) ,color = "grey") +
    geom_smooth(aes(group = rarefyID), color = "darkgrey", method = "glm", se = FALSE) +
    #geom_smooth(color = "black", method = "glm", se = FALSE) +
    geom_line(mapping = aes(y = pred)) +
    theme(legend.position = "none") +
    theme_classic() +
    ylab(ylabel)

@@

get model info
```{r}
get_metric_conint <- function(metric_name){
 data <- metrics %>%
    filter(metric == metric_name) %>%
    mutate(rarefyID = as.factor(rarefyID), logValue = log(value))

  mod <- lmer(logValue ~ year + (1|rarefyID), data = data)
  coefs <- summary(mod)$coefficients
